%\documentclass[12pt]{article}
%\usepackage[a4paper, margin=1in]{geometry} 
%\usepackage{graphicx} 
%\usepackage{hyperref}
%\usepackage{float}
%\usepackage{multicol}
%\usepackage{multirow}
%\usepackage{amsmath}
%\usepackage[font=small, labelfont=bf]{caption}
%
%\begin{document}

%
% Pattern discovery 
%
\subsection{Pattern discovery}
Sequence patterns can be created from MSAs.

%
% Pattern discovery methods
%
\subsubsection*{Pattern discovery methods}
\begin{itemize}
\item Comparison-based methods
\item Pattern-driven methods
\end{itemize}

%
% Pivot-based methods
%
\subsubsection*{Pivot-based methods}
The pivot-based method is one of the comparison-based methods.  One sequence is used as pivot, and all the rest of the sequences are compared with this pivot to find similar segments.

%
% Example of pivot-based methods
%
\subsubsection*{Example of pivot-based methods}
Find similar segments of size 3 with one edit distance without insertion/deletion for the following sequences. The first sequence should be used as pivot.

\begin{verbatim}
  Seq1 GATC
  Seq2 GGACCG
  Seq3 GAG
  Seq4 GGGT
\end{verbatim}

\noindent
Select segments for GAT.
\begin{verbatim}
  Seq2 GAC
  Seq3 GAG
  Seq4 GGT
\end{verbatim}

\noindent
Construct a pattern for the segment of GAT.
\begin{verbatim}
  G - [AG] - [CGT]
\end{verbatim}

\noindent
Select segments for ATC.
\begin{verbatim}
  Seq2 ACC
\end{verbatim}

\noindent
Construct a pattern for the segment of ATC.
\begin{verbatim}
  A - [TC] - C
\end{verbatim}

%
% Pratt
%
\subsubsection*{Pratt}
Pratt is one of the pattern-driven methods. 

$\mathrm{C_1 
-  x(i1, j1) 
-  C_2 
- x(i2, j2) 
-   \cdot\cdot\cdot 
-  C_{p-1} 
-   x(i_{p - 1}, j_{p -1})
-   C_p}$

%
% Example of Pratt
%
\subsubsection*{Example of Pratt}
Find a matched pattern for the following three sequences.
\begin{verbatim}
  Seq1 ACTG
  Seq2 ACGT
  Seq3 ACT
\end{verbatim}

$\mathrm{A - x(0,0) - C - x(0,2)}$

%
% Pratt procedure
%
\subsubsection*{Pratt procedure}
Pratt uses the following three main steps to find the best matched pattern.

\begin{itemize}
\item Preprocessing
\item Searching
\item Specialization
\end{itemize}

\bigskip 

%\end{document}
